Combinatorial Cascading Bandits with contextual information and position discounts

### 2016-01-27 contextual combinatorial cascading bandits.tex
modifications

\begin{abstract} 
We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at problem-specific criterion. In recommendation, the stopping criterion might be the first item a user selects. In network, the stopping criterion might be the first edge being blocked in a path. We also consider position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item. We propose a UCB-like algorithm to solve our problem, C$^3$-UCB, and prove a $n$-step regret bound in both the general setting and two special cases. Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discount, contextual information and partial observability. We experiment on both synthetic data and real data and show that our algorithm performs well.
\end{abstract}

@@

A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the corresponding reward. When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.

>>>>

\begin{abstract}

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then recommends a list of items, and next observes weights from the first item and stops at some problem-specific criterion. In recommendation, the stopping criterion might be the first item a user selects. In network, the stopping criterion might be the first edge being blocked in a path. We also consider position discounts in the list order, which means in recommendation the agent will receive discounted reward if the user does not select the first item. We propose a UCB-type algorithm to solve our problem, C$^3$-UCB, and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. Our work generalizes existing works and also addresses several challenges in our setting, a non-linear reward function with position discounts, contextual information and partial observability. We experiment on synthetic and real data and demonstrate the advantage to involve contextual information and position discounts.

\end{abstract}

@@

Stochastic multi-armed bandit has been extensively studied in statistics and machine learning. The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown mean. The learning agent pulls one arm every time and tries to make the cumulative regret, the expected reward difference from the best arm with highest mean, as small as possible. The problem of MAB has to deal with the trade-off between exploitation (pull the best empirical arm) and exploration (try other arms which are not sufficiently estimated).

Recently, stochastic combinatorial bandit started to draw attention \cite{gai2012combinatorial,chen2013combinatorial}. At every time step, a learning agent chooses a subset of ground items under certain combinatorial constraints and receives the corresponding reward.

When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.
